The Timing and Likelihood of the Origin of Life from Earth's Impact History

### 2023-05-10 ms.tex
added sentence to mdwarf paragraph

Beyond the early Earth, it is temping to extrapolate our result for the likelihood of the origin of life to exoplanets, however, we must do so with caution because planet's orbiting different stars may have bombardment histories unlike the Hadean. Planets in the habitable zone of an M-type star during the stellar main-sequence phase were interior to the habitable zone for several hundred million years during the super luminous pre-main-sequence phase \citep{Luger_2015}. \citet{Lichtenberg_2022} uses N-body simulations to show that, for planets hosted by M-dwarfs, large asteroid impacts are not useful for prebiotic chemistry because big impacts most likely occur within 100 million years of planet formation during the stellar pre-main-sequence when the planet is outside of the habitable zone. The pre-main-sequence phase is not an issue for an impact-induced origin of life on planets orbiting sun-like stars because the phase only lasts 10s Myrs, while large asteroid impacts occur for 100s Myrs \citep{Lichtenberg_2022}.

>>>>

It is temping to extrapolate our results beyond the early Earth to exoplanets, however, we must do so with caution because planet's orbiting different stars may have bombardment histories unlike the Hadean. Planets in the habitable zone of an M-type star during the stellar main-sequence phase were interior to the habitable zone for several hundred million years during the super luminous pre-main-sequence phase \citep{Luger_2015}. \citet{Lichtenberg_2022} uses N-body simulations to show that, for planets hosted by M-dwarfs, large asteroid impacts are not useful for prebiotic chemistry because big impacts most likely occur within 100 million years of planet formation during the stellar pre-main-sequence when the planet is outside of the habitable zone. The pre-main-sequence phase is not an issue for an impact-induced origin of life on planets orbiting sun-like stars because the phase only lasts 10s Myrs, while large asteroid impacts occur for 100s Myrs \citep{Lichtenberg_2022}. Therefore, our result that a life-starting impact was likely on the early Earth (92\% chance in an optimistic case) might be best extrapolated to habitable zone exoplanets orbiting sun-like stars.
